---
title: "adjing_cohort_split_rec_top_chr"
author: "Noah Lepola"
date: "2024-11-025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(randomForest)
library(ROCR)

```


Loading file
```{r}
load(file = "../Outputs/age_dev")
load(file = "../Outputs/pt.char")
load(file = "../Outputs/pt.status")

load(file = "../Outputs/pt.status")

```


Splitting by cohort and outcome
```{r}
train.outcomes <- filter(pt.status, Cohort == "Adj", 
Reason.for.discontinuation == "Therapy complete" |
  Reason.for.discontinuation == "Progression")
train.outcomes <- arrange(train.outcomes, desc(Sample))

test.outcomes <- filter(pt.status, Cohort == "Adj Validation",
Reason.for.discontinuation == "Therapy complete" |
  Reason.for.discontinuation == "Progression")
test.outcomes <- arrange(test.outcomes, desc(Sample))


train.seq <- filter(age_dev, (Sample %in% train.outcomes$Sample))
train.seq <- arrange(train.seq, desc(Sample))


test.seq <- filter(age_dev, (Sample %in% test.outcomes$Sample))
test.seq <- arrange(test.seq, desc(Sample))
```


Limiting information to just what is needed for this model and splitting outcome from expression
```{r}
train.seq <- train.seq %>% select(Sample, CD3D, AHR, HAVCR2, PVRIG, VTCN1, `KIR_Inhibiting_Subgroup_1`, CTLA4, CD28, GZMB, CD244, CD274, ZBTB7B, CXCR3, CD160, CD276)
test.seq <- test.seq %>% select(Sample, CD3D, AHR, HAVCR2, PVRIG, VTCN1, `KIR_Inhibiting_Subgroup_1`, CTLA4, CD28, GZMB, CD244, CD274, ZBTB7B, CXCR3, CD160, CD276)

top.c <- pt.char %>% select(Sample, `BMI (kg/m2)`)
train.seq <- left_join(train.seq, top.c)
test.seq <- left_join(test.seq, top.c)

train.outcomes <- train.outcomes %>% select(Sample, `Reason.for.discontinuation`)
test.outcomes <- test.outcomes %>% select(Sample, `Reason.for.discontinuation`)
```
top 15 genes by log regression using only Adj (exploratory) cohort CD3D, AHR, HAVCR2, PVRIG, VTCN1, `KIR_Inhibiting_Subgroup_1`, CTLA4, CD28, GZMB, CD244, CD274, ZBTB7B, CXCR3, CD160, CD276
top characteristics using only Adj (exploratory) cohort `BMI (kg/m2)`, `LDH (U/L)`, Therapy, `Platelets (K/uL)`, Age, Stage



```{r}
source("../rec_functions.R")
```

```{r}
seed_list <- c(12345:12369)
```

```{r}
#Currently working on this
r_rec_split_group_top15_chr_aucprs <- kTest(seed_list) 
r_rec_split_group_top15_chr_aucprs_avg <- mean(r_rec_split_group_top15_chr_aucprs$AUCPR)
#save(r_rec_split_group_top15_chr_aucprs, file = "../Outputs/r_rec_split_group_top15_chr_aucprs")
r_rec_split_group_top15_chr_aucprs_avg

```
