---
title: "adjing_cohort_split_group_rec_all_ad"
author: "Noah Lepola"
date: "202-1-3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(randomForest)
library(ROCR)

```

Loading file
```{r}
load(file = "../Outputs/age_dev")
load(file = "../Outputs/pt.char")
load(file = "../Outputs/pt.status")
```


Splitting by cohort and outcome
```{r}
train.outcomes <- filter(pt.status, Cohort == "Adj", 
Reason.for.discontinuation == "Therapy complete" |
  Reason.for.discontinuation == "Progression")
train.outcomes <- arrange(train.outcomes, desc(Sample))

test.outcomes <- filter(pt.status, Cohort == "Adj Validation",
Reason.for.discontinuation == "Therapy complete" |
  Reason.for.discontinuation == "Progression")
test.outcomes <- arrange(test.outcomes, desc(Sample))


train.seq <- filter(age_dev, (Sample %in% train.outcomes$Sample))
train.seq <- arrange(train.seq, desc(Sample))


test.seq <- filter(age_dev, (Sample %in% test.outcomes$Sample))
test.seq <- arrange(test.seq, desc(Sample))

```
CD3D, AHR, HAVCR2, PVRIG, VTCN1, `KIR_Inhibiting_Subgroup_1`, CTLA4, CD28, GZMB, CD244, CD274, ZBTB7B, CXCR3, CD160, CD276
Limiting information to just what is needed for this model and splitting outcome from expression
```{r}
train.seq.top <- train.seq %>% select(Sample, CD3D, AHR, HAVCR2, PVRIG, VTCN1,
`KIR_Inhibiting_Subgroup_1`, CTLA4, CD28, GZMB, CD244, CD274)

test.seq.top <- test.seq %>% select(Sample, CD3D, AHR, HAVCR2, PVRIG, VTCN1,
`KIR_Inhibiting_Subgroup_1`, CTLA4, CD28, GZMB, CD244, CD274)

top.c <- pt.char %>% select(Sample, `BMI (kg/m2)`)
train.seq.topc <- left_join(train.seq.top, top.c)
test.seq.topc <- left_join(test.seq.top, top.c)

train.outcomes <- train.outcomes %>% select(Sample, `Reason.for.discontinuation`)
test.outcomes <- test.outcomes %>% select(Sample, `Reason.for.discontinuation`)
```
Randomizing outcome
```{r}
train.random.outcomes<- train.outcomes
test.random.outcomes<- test.outcomes

train.random.outcomes$random.outcome<- (sample(train.outcomes$Reason.for.discontinuation))
test.random.outcomes$random.outcome<- (sample(test.outcomes$Reason.for.discontinuation))

```
Merging for total nanostring and outcomes
```{r}
# total.seq <- full_join(train.seq, test.seq)
# total.outcome <- full_join(train.outcomes, test.outcomes)
# 
# total.top.seq <- full_join(train.seq.top, test.seq.top)
# 
# total.topc.seq <- full_join(train.seq, test.seq)
# 
# total.random.outcome <- full_join(train.random.outcomes, test.random.outcomes)
```

```{r}
k_validate <- function(seed){
  set.seed(seed)


    out <- list()

      out[[1]] <- getROC(train.seq, train.outcomes, test.seq, test.outcomes)


  avg_aucpr <- lapply(out, function(x){ x[[1]]})
  message("\nAccuracy average: ", (rowMeans(as.data.frame(avg_aucpr))))
  return(out)
}
```

```{r}
# Function create and test RF model #
getROC <- function(train.seq, train.outcomes, test.seq, test.outcomes){
      if(all(train.seq$Sample == train.outcomes$Sample) == FALSE){
        stop("Training Sample_IDs do not match")
      }
      if(all(test.seq$Sample == test.outcomes$Sample) == FALSE){
        stop("Testing Sample_IDs do not match")
      }
  model.training <- randomForest(x = train.seq[,-1, drop=FALSE], y = as.factor(train.outcomes$Reason.for.discontinuation))
  test.preds <- predict(model.training, test.seq[,-1, drop=FALSE])

  print(model.training)
  # Check variable importance
  varImpPlot(model.training)
  # Prediction confusion matrix
  table(observed = test.outcomes$Reason.for.discontinuation, predicted = test.preds)

  prediction_for_roc_curve <- predict(model.training, test.seq[,-1, drop=FALSE],type="prob")
  pred <- prediction(prediction_for_roc_curve[,2], test.outcomes$Reason.for.discontinuation, label.ordering = c("Therapy complete", "Progression"))
  perf <- performance(pred, "tpr", "fpr")

  aucpr_ROCR <- performance(pred, measure = "aucpr")
  print(aucpr_ROCR)
  aucpr <- aucpr_ROCR@y.values[[1]]
  print(aucpr)

  df <- data.frame(FalsePositive=c(perf@x.values[[1]]),
                   TruePositive=c(perf@y.values[[1]]))
  out <- list(aucpr, df)

  return(out)
}

```

```{r}
# Grabbing AUROC values from input models #
grabVals <- function(input){
  out <- list()
   for(i in 1:length(seed_list)){
      out <- append(out, input[[i]][[1]][[1]])
   }
  out
}
```

```{r}
# Main function call to generate RF models using 25 seeds #
kTest <- function(seed_list){
  out <- list()
   for(i in 1:length(seed_list)){
    out[[i]] <- k_validate(seed = seed_list[i])
   }
  out <- grabVals(out)

  # CW edit to function
  out <- do.call(rbind.data.frame, out)
  colnames(out) <- c("AUCPR")
  out
}
```

```{r}
seed_list <- c(12345:12369)
```

```{r}
r_rec_split_group_ad_aucprs <- kTest(seed_list)
r_rec_split_group_ad_aucprs_avg <- mean(r_rec_split_group_ad_aucprs$AUCPR)
#save(r_rec_split_group_ad_aucprs, file = "../Outputs/r_rec_split_group_ad_aucprs")
r_rec_split_group_ad_aucprs_avg

```


Top genes model
```{r}
k_validate <- function(total.outcome, total.top.seq, seed){
  set.seed(seed)


    out <- list()

      out[[1]] <- getROC(train.seq.top, train.outcomes, test.seq.top, test.outcomes)


  avg_aucpr <- lapply(out, function(x){ x[[1]]})
  message("\nAccuracy average: ", (rowMeans(as.data.frame(avg_aucpr))))
  return(out)
}
```

```{r}
# Function create and test RF model #
getROC <- function(train.seq.top, train.outcomes, test.seq.top, test.outcomes){
  model.training <- randomForest(x = train.seq.top[,-1, drop=FALSE], y = as.factor(train.outcomes$Reason.for.discontinuation))
  test.preds <- predict(model.training, test.seq.top[,-1, drop=FALSE])

  print(model.training)
  # Check variable importance
  varImpPlot(model.training)
  # Prediction confusion matrix
  table(observed = test.outcomes$Reason.for.discontinuation, predicted = test.preds)

  prediction_for_roc_curve <- predict(model.training, test.seq.top[,-1, drop=FALSE],type="prob")
  pred <- prediction(prediction_for_roc_curve[,2], test.outcomes$Reason.for.discontinuation, label.ordering = c("Therapy complete", "Progression"))
  perf <- performance(pred, "tpr", "fpr")

  aucpr_ROCR <- performance(pred, measure = "aucpr")
  print(aucpr_ROCR)
  aucpr <- aucpr_ROCR@y.values[[1]]
  print(aucpr)

  df <- data.frame(FalsePositive=c(perf@x.values[[1]]),
                   TruePositive=c(perf@y.values[[1]]))
  out <- list(aucpr, df)

  return(out)
}

```

```{r}
# # Grabbing AUROC values from input models #
# grabVals <- function(input){
#   out <- list()
#    for(i in 1:length(seed_list)){
#       out <- append(out, input[[i]][[1]][[1]])
#    }
#   out
# }
```

```{r}
# Main function call to generate RF models using 25 seeds #
kTest <- function(total.outcome, total.top.seq, seed_list){
  out <- list()
   for(i in 1:length(seed_list)){
    out[[i]] <- k_validate(total.outcome, total.top.seq, seed = seed_list[i])
   }
  out <- grabVals(out)

  # CW edit to function
  out <- do.call(rbind.data.frame, out)
  colnames(out) <- c("AUCPR")
  out
}
```

```{r}
# seed_list <- c(12345:12369)
```


```{r}
r_rec_split_top12_group_ad_aucprs <- kTest(total.outcome, total.top.seq, seed_list)
r_rec_split_top12_group_ad_aucprs_avg <- mean(r_rec_split_top12_group_ad_aucprs$AUCPR)
#save(r_rec_split_top12_group_ad_aucprs, file = "../Outputs/r_rec_split_top12_group_ad_aucprs")
r_rec_split_top12_group_ad_aucprs_avg

```


Top genes and characteristic model
```{r}
k_validate <- function(total.outcome, total.topc.seq, seed){
  set.seed(seed)
  

    out <- list()

      out[[1]] <- getROC(train.seq.topc, train.outcomes, test.seq.topc, test.outcomes)

  
  avg_aucpr <- lapply(out, function(x){ x[[1]]})
  message("\nAccuracy average: ", (rowMeans(as.data.frame(avg_aucpr))))
  return(out)
}
```

```{r}
# Function create and test RF model #
getROC <- function(train.seq.topc, train.outcomes, test.seq.topc, test.outcomes){
  model.training <- randomForest(x = train.seq.topc[,-1, drop=FALSE], y = as.factor(train.outcomes$Reason.for.discontinuation))
  test.preds <- predict(model.training, test.seq.topc[,-1, drop=FALSE])
  
  print(model.training)
  # Check variable importance
  varImpPlot(model.training)
  # Prediction confusion matrix
  table(observed = test.outcomes$Reason.for.discontinuation, predicted = test.preds)
  
  prediction_for_roc_curve <- predict(model.training, test.seq.topc[,-1, drop=FALSE],type="prob")
  pred <- prediction(prediction_for_roc_curve[,2], test.outcomes$Reason.for.discontinuation, label.ordering = c("Therapy complete", "Progression"))
  perf <- performance(pred, "tpr", "fpr")
  
  aucpr_ROCR <- performance(pred, measure = "aucpr")
  print(aucpr_ROCR)
  aucpr <- aucpr_ROCR@y.values[[1]]
  print(aucpr)
  
  df <- data.frame(FalsePositive=c(perf@x.values[[1]]),
                   TruePositive=c(perf@y.values[[1]]))
  out <- list(aucpr, df)
  
  return(out)
}

```

```{r}
# # Grabbing AUROC values from input models #
# grabVals <- function(input){
#   out <- list()
#    for(i in 1:length(seed_list)){
#       out <- append(out, input[[i]][[1]][[1]])
#    }
#   out
# }
```

```{r}
# Main function call to generate RF models using 25 seeds #
kTest <- function(total.outcome, total.topc.seq, seed_list){
  out <- list()
   for(i in 1:length(seed_list)){
    out[[i]] <- k_validate(total.outcome, total.topc.seq, seed = seed_list[i])
   }
  out <- grabVals(out)
  
  # CW edit to function 
  out <- do.call(rbind.data.frame, out)
  colnames(out) <- c("AUCPR")
  out
}
```

```{r}
# seed_list <- c(12345:12369)
```

```{r}
r_rec_split_group_top12_chr_ad_aucprs <- kTest(total.outcome, total.topc.seq, seed_list) 
r_rec_split_group_top12_chr_ad_aucprs_avg <- mean(r_rec_split_group_top12_chr_ad_aucprs$AUCPR)
#save(r_rec_split_group_top12_chr_ad_aucprs, file = "../Outputs/r_rec_split_group_top12_chr_ad_aucprs")
r_rec_split_group_top12_chr_ad_aucprs_avg

```


Model with random outcomes
```{r}
k_validate <- function(total.random.outcome, total.seq, seed){
  set.seed(seed)
  

    out <- list()

      out[[1]] <- getROC(train.seq, train.random.outcomes, test.seq, test.random.outcomes)

  
  avg_aucpr <- lapply(out, function(x){ x[[1]]})
  message("\nAccuracy average: ", (rowMeans(as.data.frame(avg_aucpr))))
  return(out)
}
```

```{r}
# Function create and test RF model #
getROC <- function(train.seq, train.random.outcomes, test.seq, test.random.outcomes){
  model.training <- randomForest(x = train.seq[,-1, drop=FALSE], y = as.factor(train.random.outcomes$random.outcome))
  test.preds <- predict(model.training, test.seq[,-1, drop=FALSE])
  
  # print(model.training)
  # Check variable importance
  # varImpPlot(model.training)
  # Prediction confusion matrix
  table(observed = test.random.outcomes$random.outcome, predicted = test.preds)
  
  prediction_for_roc_curve <- predict(model.training, test.seq[,-1, drop=FALSE],type="prob")
  pred <- prediction(prediction_for_roc_curve[,2], test.random.outcomes$random.outcome, label.ordering = c("Therapy complete", "Progression"))
  perf <- performance(pred, "tpr", "fpr")
  
  aucpr_ROCR <- performance(pred, measure = "aucpr")
  print(aucpr_ROCR)
  aucpr <- aucpr_ROCR@y.values[[1]]
  print(aucpr)
  
  df <- data.frame(FalsePositive=c(perf@x.values[[1]]),
                   TruePositive=c(perf@y.values[[1]]))
  out <- list(aucpr, df)
  
  return(out)
}

```

```{r}
# # Grabbing AUROC values from input models #
# grabVals <- function(input){
#   out <- list()
#    for(i in 1:length(seed_list_r)){
#       out <- append(out, input[[i]][[1]][[1]])
#    }
#   out
# }
```

```{r}
# Main function call to generate RF models using 25 seeds #
kTest <- function(total.random.outcome, total.seq, seed_list_r){
  out <- list()
   for(i in 1:length(seed_list_r)){
    out[[i]] <- k_validate(total.random.outcome, total.seq, seed = seed_list_r[i])
   }
  out <- grabVals(out)
  
  # CW edit to function 
  out <- do.call(rbind.data.frame, out)
  colnames(out) <- c("AUCPR")
  out
}
```

```{r}
seed_list_r <- c(12345:12844)
```

```{r}
r_random_rec_split_group_ad_aucprs <- kTest(response, sampledata, seed_list_r) 
r_random_rec_split_group_ad_aucprs_avg <- mean(r_random_rec_split_group_ad_aucprs$AUCPR)
#save(r_random_rec_split_group_ad_aucprs, file = "../Outputs/r_random_rec_split_group_ad_aucprs")
r_random_rec_split_group_ad_aucprs_avg

```
