---
title: "adj_cohort_split_group_tox_top02_chr"
author: "Noah Lepola"
date: "2024-11-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(randomForest)
library(ROCR)



```

```{r}
load(file = "../Outputs/gene.exp")
load(file = "../Outputs/pt.char")
load(file = "../Outputs/pt.status")
```


Splitting by cohort and outcome
```{r}
train.outcomes <- filter(pt.status, Cohort == "Adj", 
Reason.for.discontinuation == "Therapy complete" |
  Reason.for.discontinuation == "Toxicity")
train.outcomes <- arrange(train.outcomes, desc(Sample))

test.outcomes <- filter(pt.status, Cohort == "Adj Validation",
Reason.for.discontinuation == "Therapy complete" |
  Reason.for.discontinuation == "Toxicity")
test.outcomes <- arrange(test.outcomes, desc(Sample))


train.seq <- filter(gene.exp, (Sample %in% train.outcomes$Sample))
train.seq <- arrange(train.seq, desc(Sample))


test.seq <- filter(gene.exp, (Sample %in% test.outcomes$Sample))
test.seq <- arrange(test.seq, desc(Sample))
```

top 10 genes by log regression TNFRSF18, VTCN1, NECTIN2, AHR, FOXO1, CCR4, RUNX3, `IL-2`, CD28, TIGIT
top 15 genes by log regression using only Adj (exploratory) cohort PDCD1LG2, NECTIN2, `KIR_Inhibiting_Subgroup_2`, RUNX3, CDKN1B, B3GAT1, HPRT1, HAVCR2, `PTPRC_1`, `IL-10`, GZMB, TNF, TBX21, CCR4, PGK1
top characteristics using only Adj (exploratory) cohort Therapy, `BMI (kg/m2)`, `Platelets (K/uL)`, `LDH (U/L)`, Stage, Age


Limiting to most differential genes and characteristics (2 and 5 respectively) as determined by logistic regression as narrowing it to those produced the highest AUCPR 
```{r}
train.seq <- train.seq %>% select(Sample, PDCD1LG2, NECTIN2)
test.seq <- test.seq %>% select(Sample, PDCD1LG2, NECTIN2)

top.c <- pt.char %>% select(Sample, Therapy, `BMI (kg/m2)`, `Platelets (K/uL)`,
                            `LDH (U/L)`, Stage, Age)
train.seq <- left_join(train.seq, top.c)
test.seq <- left_join(test.seq, top.c)

train.outcomes <- train.outcomes %>% select(Sample, `Reason.for.discontinuation`)
test.outcomes <- test.outcomes %>% select(Sample, `Reason.for.discontinuation`)
```



```{r}
source("../tox_functions.R")
```

```{r}
seed_list <- c(12345:12369)
```

```{r}
#Currently working on this
r_tox_split_group_top02_chr_aucprs <- kTest(seed_list) 
r_tox_split_group_top02_chr_aucprs_avg <- mean(r_tox_split_group_top02_chr_aucprs$AUCPR)
#save(r_tox_split_group_top02_chr_aucprs, file = "../Outputs/r_tox_split_group_top02_chr_aucprs")
r_tox_split_group_top02_chr_aucprs_avg

```
