---
title: "adjing_cohort_split_rec_top_chr"
author: "Noah Lepola"
date: "2024-11-025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(randomForest)
library(ROCR)

```


Loading file
```{r}
load(file = "age_dev")
load(file = "pt.char")
load(file = "pt.status")
```


Splitting by cohort and outcome
```{r}
train.outcomes <- filter(pt.status, Cohort == "Adj", 
Reason.for.discontinuation == "Therapy complete" |
  Reason.for.discontinuation == "Progression")
train.outcomes <- arrange(train.outcomes, desc(Sample))

test.outcomes <- filter(pt.status, Cohort == "Adj Validation",
Reason.for.discontinuation == "Therapy complete" |
  Reason.for.discontinuation == "Progression")
test.outcomes <- arrange(test.outcomes, desc(Sample))


train.seq <- filter(age_dev, (Sample %in% train.outcomes$Sample))
train.seq <- arrange(train.seq, desc(Sample))


test.seq <- filter(age_dev, (Sample %in% test.outcomes$Sample))
test.seq <- arrange(test.seq, desc(Sample))
```


Limiting information to just what is needed for this model and splitting outcome from expression
```{r}
train.seq <- train.seq %>% select(Sample, CD3D, AHR, HAVCR2, PVRIG, VTCN1,
 `KIR_Inhibiting_Subgroup_1`, CTLA4, CD28, GZMB, CD244, CD274, ZBTB7B, CXCR3)


test.seq <- test.seq %>% select(Sample, CD3D, AHR, HAVCR2, PVRIG, VTCN1, 
 `KIR_Inhibiting_Subgroup_1`, CTLA4, CD28, GZMB, CD244, CD274, ZBTB7B, CXCR3)

top.c <- pt.char %>% select(Sample, `BMI (kg/m2)`, `LDH (U/L)`, Therapy, 
                            `Platelets (K/uL)`, Age)
train.seq <- left_join(train.seq, top.c)
test.seq <- left_join(test.seq, top.c)

train.outcomes <- train.outcomes %>% select(Sample, `Reason.for.discontinuation`)
test.outcomes <- test.outcomes %>% select(Sample, `Reason.for.discontinuation`)
```
top 15 genes by log regression using only Adj (exploratory) cohort CD3D, AHR, HAVCR2, PVRIG, VTCN1, `KIR_Inhibiting_Subgroup_1`, CTLA4, CD28, GZMB, CD244, CD274, ZBTB7B, CXCR3, CD160, CD276
top characteristics using only Adj (exploratory) cohort `BMI (kg/m2)`, `LDH (U/L)`, Therapy, `Platelets (K/uL)`, Age, Stage



```{r}
source("rec_functions.R")
```

```{r}
seed_list <- c(12345:12369)
```

```{r}
#Currently working on this
rf_ad_rec_top_char_aucprs <- kTest(seed_list) 
rf_ad_rec_top_char_aucprs_avg <- mean(rf_ad_rec_top_char_aucprs$AUCPR)
write.csv(rf_ad_rec_top_char_aucprs, file = "rf_ad_rec_top_char_aucprs.csv")
rf_ad_rec_top_char_aucprs_avg

```



```{r}
run_number <- 1:1000
seed_list_r <- c(12345:13344)
rf_ad_rec_top_char_random_1000 <- data.frame(run = run_number, Average = NA)
```

```{r}
for (j in 1:length(run_number)) {
  set.seed(seed_list_r[j])
train.outcomes$Reason.for.discontinuation<- 
  (sample(train.outcomes$Reason.for.discontinuation))

test.outcomes$Reason.for.discontinuation<- 
  (sample(test.outcomes$Reason.for.discontinuation))

r_random_rec_aucprs <- kTest(seed_list) 
avg <- mean(r_random_rec_aucprs$AUCPR)
rf_ad_rec_top_char_random_1000[j, 2] <- avg

  }
mean(rf_ad_rec_top_char_random_1000$Average)

write.csv(rf_ad_rec_top_char_random_1000, file = "rf_ad_rec_top_char_random_1000.csv")
```



