---
title: "Additional metrics script"
author: "Noah Lepola"
date: "2025-03-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(caret)
library(tidyverse)
library(ggplot2)

#table one aesthetics and export, adjing test met genes from Jason paper. Also remove 0s. Clinical compairons 

```

```{r}
source("../rf_functions.R")
```

Loading all the files needed. First in each section is the actual run data, second is the 1000x random shuffle runs



Creating a function to get the average from each run of the 1000x random and then calculate the percentile of the normal run
#p calc function
```{r}
met.p.calc <- function(randomdata, pos.outcome, output, dataobject){
#function that generates averages of metrics for randomized run
  random_met <- add.metrics(randomdata,
                            random_met,
                            pos.outcome)
  

#storing experimental run additional metrics   
    temp_conmat2 <- data.frame(run = 1:25,
                               Accuracy = NA,
                               Specificity = NA,
                               Precision = NA,
                               Recall = NA,
                               F1 = NA)
    
#generating additional metrics for experimental run    
  for (i in 1:25) {
    temp_conmat <- confusionMatrix(dataobject[[i]][[1]][[3]],
                                   positive = pos.outcome)
    
    temp_conmat2$Accuracy[i] <- temp_conmat[[3]][1]
    
    temp_conmat2$Specificity[i] <- temp_conmat[[4]][2]
    
    temp_conmat2$Precision[i] <- temp_conmat[[4]][5]
    
    temp_conmat2$Recall[i] <- temp_conmat[[4]][6]
    
    temp_conmat2$F1[i] <- temp_conmat[[4]][7]
    
  }
    print(mean(temp_conmat2$Accuracy))
    print(mean(temp_conmat2$Specificity))
    print(mean(temp_conmat2$Precision))
    print(mean(temp_conmat2$Recall))
    print(mean(temp_conmat2$F1))
#storing percentiles    
    output <- data.frame(Accuracy = NA,
                         Specificity = NA,
                         Precision = NA,
                         Recall = NA,
                         F1 = NA)
    
#converting NAs to 0 so we don't skew the averages    
      # temp_conmat2[is.na(temp_conmat2)] <- 0
      
#percentile calculation for various metrics  
      
avg.acc <- mean(temp_conmat2$Accuracy)
output$Accuracy[1] <- p.calc(avg.acc,
                             random_met$Avg.Accuracy)

avg.s <- mean(temp_conmat2$Specificity)
output$Specificity[1] <- p.calc(avg.s,
                                random_met$Avg.Specificity)

avg.prec <- mean(temp_conmat2$Precision)
output$Precision[1] <- p.calc(avg.prec,
                              random_met$Avg.Precision)

avg.recall <- mean(temp_conmat2$Recall)
output$Recall[1] <- p.calc(avg.recall,
                           random_met$Avg.Recall)

avg.F1 <- mean(temp_conmat2$F1)
avg.F1[is.na(avg.F1)] <- 0

output$F1[1] <- p.calc(avg.F1,
                       random_met$Avg.F1)


print(output$F1)

# data_wide <- full_join(random_met, temp_conmat2)
# data_wide <- select(data_wide, -run)
# data_graph <- data_wide %>% 
#   gather(key="RunVersion", value="Val") %>%
#   ggplot( aes(x=RunVersion, y=Val, fill=RunVersion)) +
#     geom_violin()
# 
# print(data_graph)

output
}
```



```{r}




# f1.rec <- c("Full panel", "CD160-VTCN1", "Metastatic")
# f1.tox <- c("Full panel", "TNFRSF18-VTCN1-CCR4-AHR-TIGIT", "Metastatic")
# 
# f1.tox.df <- data.frame(Model = f1.tox,
#                             "Average F1 Percentile" = NA)
# f1.tox.df$Average.F1.Percentile[1] <- tox_noipi_perc$F1
# f1.tox.df$Average.F1.Percentile[2] <- tox_5_noipi_perc$F1
# f1.tox.df$Average.F1.Percentile[3] <- tox_met_5_noipi_perc$F1
# 
# 
# f1.rec.df <- data.frame(Model = f1.rec,
#                             "Average F1 Percentile" = NA)
# f1.rec.df$Average.F1.Percentile[1] <- rec_noipi_perc$F1
# f1.rec.df$Average.F1.Percentile[2] <- rec_2_noipi_perc$F1
# f1.rec.df$Average.F1.Percentile[3] <- rec_met_2_noipi_perc$F1

```

#metric_graph
```{r}
metric_graph <- function(randomdata, pos.outcome, dataobject, percentile, titlename, yvalue){

metricsdf <- add.metrics(randomdata,
                          metricsdf,
                          pos.outcome)

    modelmetricsdf <- data.frame(run = 1:25,
                             Accuracy = NA,
                             Specificity = NA,
                             Precision = NA,
                             Recall = NA,
                             F1 = NA)


  for (i in 1:25) {
  temp_conmat <- confusionMatrix(dataobject[[i]][[1]][[3]],
                                 positive = pos.outcome)

  modelmetricsdf$Accuracy[i] <- temp_conmat[[3]][1]

  modelmetricsdf$Specificity[i] <- temp_conmat[[4]][2]

  modelmetricsdf$Precision[i] <- temp_conmat[[4]][5]

  modelmetricsdf$Recall[i] <- temp_conmat[[4]][6]

  modelmetricsdf$F1[i] <- temp_conmat[[4]][7]
  }

modelmetricsdf.avg.F1<- mean(modelmetricsdf$F1)
modelmetricsdf.avg.F1[is.na(modelmetricsdf.avg.F1)] <- 0

# metricsdf <- metricsdf %>%
#   filter(Avg.F1 != 0)

# metrics_plot <- ggplot(data = metricsdf, aes(x = Avg.F1)) + 
#   geom_density() +
#   geom_vline(xintercept = modelmetricsdf.avg.F1, color = "red")

metrics_plot <- ggplot(data = metricsdf, aes(x = Avg.F1)) + 
  geom_density(fill = "skyblue", alpha = 0.4, linewidth = 0.75) + 
  geom_vline(aes(xintercept = modelmetricsdf.avg.F1), 
             color = "red", 
             linetype = "dashed", 
             linewidth = 2) +
annotate("text", 
           x = modelmetricsdf.avg.F1, 
           y = yvalue, 
           label = paste0("Model Performance\n", percentile), # \n creates the second line
           color = "red", 
           angle = 90, 
           size = 7, 
           vjust = 1.2,     # Moves text horizontally relative to the line
           hjust = 0.5) +   # Centers the text vertically along the line (since angle=90) +
  labs(
    title = titlename,
       x = "Performance (F1 Score)",
       y = "Density of random data runs") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(size = 22, face = "bold", margin = ggplot2::margin(t = 10)),
    axis.title.y = element_text(size = 22, face = "bold", margin = ggplot2::margin(r = 10)),
    axis.text = element_text(size = 20),  
    plot.title = element_text(size = 26, face = "bold", hjust = 0.5)
  ) 


print(metrics_plot)
}
```




#rec clinical
```{r}
rf_rec_noipi_clinical <- readRDS(file = "../Outputs/rf_rec_noipi_clinical.RData")
rf_rec_noipi_clinical_random_25000 <- readRDS(file = "../Outputs/rf_rec_noipi_clinical_random_25000.RData")

rec.clinical <- met.p.calc(rf_rec_noipi_clinical_random_25000,
                        "Progression",
                       rec.clinical,
                       rf_rec_noipi_clinical
                       )


metric_graph(rf_rec_noipi_clinical_random_25000,
             "Progression", 
             rf_rec_noipi_clinical,
             NULL, 
             "Clinical Characteristics",
             3)
```




#rec total graph
```{r}
rf_rec_noipi <- readRDS(file = "../Outputs/rf_rec_noipi.RData")
rf_rec_noipi_random_25000 <- readRDS(file = "../Outputs/rf_rec_noipi_random_25000.RData")

rec.allgenes <- met.p.calc(rf_rec_noipi_random_25000,
                        "Progression",
                       rec.allgenes,
                       rf_rec_noipi)


metric_graph(rf_rec_noipi_random_25000,
             "Progression",
             rf_rec_noipi,
             "(64.2 %ile)", 
             "All mRNA",
             2)

```




#rec top 2
```{r}
rf_rec_top_2_noipi <- readRDS(file = "../Outputs/rf_rec_top_2_noipi.RData")
rf_rec_top_random_2_noipi_25000 <- readRDS(file = "../Outputs/rf_rec_top_random_2_noipi_25000.RData")

rec.top2 <- met.p.calc(rf_rec_top_random_2_noipi_25000,
                        "Progression",
                       rec.top2,
                       rf_rec_top_2_noipi)



metric_graph(rf_rec_top_random_2_noipi_25000,
             "Progression",
             rf_rec_top_2_noipi,
             "(95.1 %ile)", 
             "CD160-GZMB",
             1.75)
```


#rec boruta 1
```{r}
rf_rec_boruta_1_noipi <- readRDS(file = "../Outputs/rf_rec_boruta_1_noipi.RData")
rf_rec_boruta_random_1_noipi_25000 <- readRDS(file = "../Outputs/rf_rec_boruta_random_1_noipi_25000.RData")

rec.boruta1 <- met.p.calc(rf_rec_boruta_random_1_noipi_25000,
                        "Progression",
                       rec.boruta1,
                       rf_rec_boruta_1_noipi)



metric_graph(rf_rec_boruta_random_1_noipi_25000,
             "Progression",
             rf_rec_boruta_1_noipi,
             "(18.1 %ile)", 
             "CD160",
             1.75)
```


#rec full list boruta low
```{r}
rf_rec_fulllow_boruta_10_noipi <- readRDS(file = "../Outputs/rf_rec_fulllow_boruta_10_noipi.RData")
rf_rec_fulllow_boruta_random_10_noipi_25000 <- readRDS(file = "../Outputs/rf_rec_fulllow_boruta_random_10_noipi_25000.RData")

rec.borutalow <- met.p.calc(rf_rec_fulllow_boruta_random_10_noipi_25000,
                        "Progression",
                       rec.borutalow,
                       rf_rec_fulllow_boruta_10_noipi)



metric_graph(rf_rec_fulllow_boruta_random_10_noipi_25000,
             "Progression",
             rf_rec_fulllow_boruta_10_noipi,
             "(82.9 %ile)", 
             "10 mRNAS",
             1.75)
```



#rec full listboruta med Majority model
```{r}
rf_rec_fullmed_boruta_7_noipi <- readRDS(file = "../Outputs/rf_rec_fullmed_boruta_7_noipi.RData")
rf_rec_fullmed_boruta_random_7_noipi_25000 <- readRDS(file = "../Outputs/rf_rec_fullmed_boruta_random_7_noipi_25000.RData")

rec.borutamed <- met.p.calc(rf_rec_fullmed_boruta_random_7_noipi_25000,
                        "Progression",
                       rec.borutamed,
                       rf_rec_fullmed_boruta_7_noipi)



metric_graph(rf_rec_fullmed_boruta_random_7_noipi_25000,
             "Progression",
             rf_rec_fullmed_boruta_7_noipi,
             "(85.7 %ile)", 
             "Boruta-Majority of runs",
             2)
```


#rec full list boruta high
```{r}
rf_rec_fullhigh_boruta_4_noipi <- readRDS(file = "../Outputs/rf_rec_fullhigh_boruta_4_noipi.RData")
rf_rec_fullhigh_boruta_random_4_noipi_25000 <- readRDS(file = "../Outputs/rf_rec_fullhigh_boruta_random_4_noipi_25000.RData")

rec.borutahigh <- met.p.calc(rf_rec_fullhigh_boruta_random_4_noipi_25000,
                        "Progression",
                       rec.borutahigh,
                       rf_rec_fullhigh_boruta_4_noipi)



metric_graph(rf_rec_fullhigh_boruta_random_4_noipi_25000,
             "Progression",
             rf_rec_fullhigh_boruta_4_noipi,
             "(83.3 %ile)", 
             "4 mRNAs",
             1.75)
```

#Meta pro clinical
```{r}
rf_pro_meta_clinical <- readRDS(file = "../Outputs/rf_pro_meta_clinical.RData")
rf_pro_meta_clinical_random_25000 <- readRDS(file = "../Outputs/rf_pro_meta_clinical_random_25000.RData")

pro.clinical <- met.p.calc(rf_pro_meta_clinical_random_25000,
                        "Progression",
                       pro.clinical,
                       rf_pro_meta_clinical)



metric_graph(rf_pro_meta_clinical_random_25000,
             "Progression",
             rf_pro_meta_clinical,
             "(67.3 %ile)", 
             "Clinical",
             1.75)

```



#Meta pro total
```{r}
rf_pro_meta <- readRDS(file = "../Outputs/rf_pro_meta.RData")
rf_pro_meta_random_25000 <- readRDS(file = "../Outputs/rf_pro_meta_random_25000.RData")

pro.total <- met.p.calc(rf_pro_meta_random_25000,
                        "Progression",
                       pro.total,
                       rf_pro_meta)



metric_graph(rf_pro_meta_random_25000,
             "Progression",
             rf_pro_meta,
             "(50.2 %ile)", 
             "All mRNA",
             1.5)

```



#Meta pro full top list
```{r}
rf_pro_meta_fulltoplist <- readRDS(file = "../Outputs/rf_pro_meta_fulltoplist.RData")
rf_pro_meta_fulltoplist_random_25000 <- readRDS(file = "../Outputs/rf_pro_meta_random_25000.RData")

pro.fulltoplist <- met.p.calc(rf_pro_meta_fulltoplist_random_25000,
                        "Progression",
                       pro.fulltoplist,
                       rf_pro_meta_fulltoplist)



metric_graph(rf_pro_meta_fulltoplist_random_25000,
             "Progression",
             rf_pro_meta_fulltoplist,
             "(57.3 %ile)", 
             "Top 41 genes",
             1.25)

```


#Meta pro boruta list
```{r}
rf_pro_meta_boruta_2 <- readRDS(file = "../Outputs/rf_pro_meta_boruta_2.RData")
rf_pro_meta_random_boruta_2_25000 <- readRDS(file = "../Outputs/rf_pro_meta_random_boruta_2_25000.RData")

pro.boruta <- met.p.calc(rf_pro_meta_random_boruta_2_25000,
                        "Progression",
                       pro.boruta,
                       rf_pro_meta_boruta_2)



metric_graph(rf_pro_meta_random_boruta_2_25000,
             "Progression",
             rf_pro_meta_boruta_2,
             "(24.3 %ile)", 
             "IL-21 - PVR",
             1.75)

```





#Meta pro low boruta list
```{r}
rf_pro_meta_low_boruta_5 <- readRDS(file = "../Outputs/rf_pro_meta_low_boruta_5.RData")
rf_pro_meta_low_random_boruta_5_25000 <- readRDS(file = "../Outputs/rf_pro_meta_low_random_boruta_5_25000.RData")

pro.borutalow <- met.p.calc(rf_pro_meta_low_random_boruta_5_25000,
                        "Progression",
                       pro.borutalow,
                       rf_pro_meta_low_boruta_5)



metric_graph(rf_pro_meta_low_random_boruta_5_25000,
             "Progression",
             rf_pro_meta_low_boruta_5,
             "(66.6 %ile)", 
             "5 mRNAs",
             1.25)

```


#Meta pro high boruta list
```{r}
rf_pro_meta_high_boruta_1 <- readRDS(file = "../Outputs/rf_pro_meta_high_boruta_1.RData")
rf_pro_meta_high_random_boruta_1_25000 <- readRDS(file = "../Outputs/rf_pro_meta_high_random_boruta_1_25000.RData")

pro.borutahigh <- met.p.calc(rf_pro_meta_high_random_boruta_1_25000,
                        "Progression",
                       pro.borutahigh,
                       rf_pro_meta_high_boruta_1)



metric_graph(rf_pro_meta_high_random_boruta_1_25000,
             "Progression",
             rf_pro_meta_high_boruta_1,
             "(93.6 %ile)", 
             "1 mRNA",
             1.75)

```


#Meta pro fulllow boruta list
```{r}
rf_pro_meta_fulllow_boruta_6 <- readRDS(file = "../Outputs/rf_pro_meta_fulllow_boruta_6.RData")
rf_pro_meta_fulllow_random_boruta_6_25000 <- readRDS(file = "../Outputs/rf_pro_meta_fulllow_random_boruta_6_25000.RData")

pro.borutafulllow <- met.p.calc(rf_pro_meta_fulllow_random_boruta_6_25000,
                        "Progression",
                       pro.borutafulllow,
                       rf_pro_meta_fulllow_boruta_6)



metric_graph(rf_pro_meta_fulllow_random_boruta_6_25000,
             "Progression",
             rf_pro_meta_fulllow_boruta_6,
             "(85.6 %ile)", 
             "6 mRNAs",
             1.25)

```


#Meta pro fullhigh boruta list
```{r}
rf_pro_meta_fullhigh_boruta_1 <- readRDS(file = "../Outputs/rf_pro_meta_fullhigh_boruta_1.RData")
rf_pro_meta_fullhigh_random_boruta_1_25000 <- readRDS(file = "../Outputs/rf_pro_meta_fullhigh_random_boruta_1_25000.RData")

pro.borutafullhigh <- met.p.calc(rf_pro_meta_fullhigh_random_boruta_1_25000,
                        "Progression",
                       pro.borutafullhigh,
                       rf_pro_meta_fullhigh_boruta_1)



metric_graph(rf_pro_meta_fullhigh_random_boruta_1_25000,
             "Progression",
             rf_pro_meta_fullhigh_boruta_1,
             "(93.6 %ile)", 
             "Boruta-Majority of runs",
             1.55)

```

#Meta pro limited list
```{r}
rf_pro_meta_limited_1 <- readRDS(file = "../Outputs/rf_pro_meta_limitedlist.RData")
rf_pro_meta_random_limited_1_25000 <- readRDS(file = "../Outputs/rf_pro_meta_limitedlist_random_25000.RData")

pro.boruta <- met.p.calc(rf_pro_meta_random_limited_1_25000,
                        "Progression",
                       pro.boruta,
                       rf_pro_meta_limited_1)



metric_graph(rf_pro_meta_random_limited_1_25000,
             "Progression",
             rf_pro_meta_limited_1,
             "(66.7 %ile)", 
             "IL-4",
             1.75)

```




#rec train meta test rec/pro
```{r}
rf_pro_adjtrain_metatest <- readRDS(file = "../Outputs/rf_rec_top_metapro.RData")
rf_pro_adjtrain_metatest_random <- readRDS(file = "../Outputs/rf_rec_top_random_metapro_25000.RData")

adj_train_rec <- met.p.calc(rf_pro_adjtrain_metatest_random,
                        "Progression",
                       adj_train_rec,
                       rf_pro_adjtrain_metatest)



metric_graph(rf_pro_adjtrain_metatest_random,
             "Progression",
             rf_pro_adjtrain_metatest,
             "(82.3 %ile)", 
             "Adj Train Meta Test Pro",
             1.25)
```



#meta train rec test rec/pro
```{r}
rf_pro_metatrain_adjtest <- readRDS(file = "../Outputs/rf_pro_meta_fulltoplist_adjrec.RData")
rf_pro_metatrain_adjtest_random <- readRDS(file = "../Outputs/rf_pro_meta_fulltoplist_adjrec_random_25000.RData")

meta_train_pro <- met.p.calc(rf_pro_metatrain_adjtest_random,
                        "Progression",
                       meta_train_pro,
                       rf_pro_metatrain_adjtest)



metric_graph(rf_pro_metatrain_adjtest_random,
             "Progression",
             rf_pro_metatrain_adjtest,
             "(83.5 %ile)", 
             "Meta Train Adj Test Rec",
             2)
```




#rec top 3 metagenes
```{r}
rf_rec_metgenes_3_noipi <- readRDS(file = "../Outputs/rf_rec_metgenes_3_noipi.RData")
rf_rec_metgenes_random_3_noipi_25000 <- readRDS(file = "../Outputs/rf_rec_metgenes_random_3_noipi_25000.RData")

rec.metagenes <- met.p.calc(rf_rec_metgenes_random_3_noipi_25000,
                        "Progression",
                       rec.metagenes,
                       rf_rec_metgenes_3_noipi)



metric_graph(rf_rec_metgenes_random_3_noipi_25000,
             "Progression",
             rf_rec_metgenes_3_noipi,
             NULL, 
             "CD8A-CD45RB-TNFRSF14",
             2.5)
```



#rec top 2 metastatic
```{r}
rf_met_rec_noipi_top_2_0 <- readRDS(file = "../Outputs/rf_met_rec_noipi_top_2_0.RData")
rf_met_rec_noipi_top_random_2_0_25000 <- readRDS(file = "../Outputs/rf_met_rec_noipi_top_random_2_0_25000.RData")

rec.metastatic <- met.p.calc(rf_met_rec_noipi_top_random_2_0_25000,
                        "Progression",
                       rec.metastatic,
                       rf_met_rec_noipi_top_2_0)



metric_graph(rf_met_rec_noipi_top_random_2_0_25000,
             "Progression",
             rf_met_rec_noipi_top_2_0,
             "(48.2 %ile)", 
             "CD160-GZMB",
             1)
```


#tox clinical
```{r}
rf_tox_noipi_clinical <- readRDS(file = "../Outputs/rf_tox_noipi_clinical.RData")
rf_tox_noipi_clinical_random_25000 <- readRDS(file = "../Outputs/rf_tox_noipi_clinical_random_25000.RData")

tox.clinical <- met.p.calc(rf_tox_noipi_clinical_random_25000,
                        "Toxicity",
                       tox.clinical,
                       rf_tox_noipi_clinical)



metric_graph(rf_tox_noipi_clinical_random_25000,
             "Toxicity",
             rf_tox_noipi_clinical,
             NULL, 
             "Clinical Characteristics",
             4.4)

```


#tox total graph
```{r}
rf_tox_noipi <- readRDS(file = "../Outputs/rf_tox_noipi.RData")
rf_tox_noipi_random_25000 <- readRDS(file = "../Outputs/rf_tox_noipi_random_25000.RData")

tox.allgenes <- met.p.calc(rf_tox_noipi_random_25000,
                        "Toxicity",
                       tox.allgenes,
                       rf_tox_noipi)


metric_graph(rf_tox_noipi_random_25000,
             "Toxicity",
             rf_tox_noipi,
             "(94.0 %ile)", 
             "All mRNA",
             1.5)
```


#tox top 5 graph
```{r}
rf_tox_top_noipi_5 <- readRDS(file = "../Outputs/rf_tox_top_noipi_5.RData")
rf_tox_top_noipi_random_5_25000 <- readRDS(file = "../Outputs/rf_tox_top_noipi_random_5_25000.RData")

tox.top5 <- met.p.calc(rf_tox_top_noipi_random_5_25000,
                        "Toxicity",
                       tox.top5,
                       rf_tox_top_noipi_5)



metric_graph(rf_tox_top_noipi_random_5_25000,
             "Toxicity",
             rf_tox_top_noipi_5,
             "(97.4 %ile)", 
             "TNFRSF18-VTCN1-CCR4-AHR-TIGIT",
             2)
```


#tox best model logr
```{r}
rf_tox_bestlogr <- readRDS(file = "../Outputs/rf_tox_top_noipi_best_35.RData")
rf_tox_bestlogr_25000 <- readRDS(file = "../Outputs/rf_tox_top_noipi_random_best_35_25000.RData")

tox.bestlogr <- met.p.calc(rf_tox_bestlogr_25000,
                        "Toxicity",
                       tox.bestlogr,
                       rf_tox_bestlogr)



metric_graph(rf_tox_bestlogr_25000,
             "Toxicity",
             rf_tox_bestlogr,
             "(98 %ile)", 
             "Toxicity-Highest Logr F1 model",
             2)
```


#tox boruta 6 graph
```{r}
rf_tox_boruta_noipi_6 <- readRDS(file = "../Outputs/rf_tox_top_noipi_boruta_6.RData")
rf_tox_top_boruta_random_6_25000 <- readRDS(file = "../Outputs/rf_tox_top_noipi_random_boruta_6_25000.RData")

tox.boruta6 <- met.p.calc(rf_tox_top_boruta_random_6_25000,
                        "Toxicity",
                       tox.boruta6,
                       rf_tox_boruta_noipi_6)



metric_graph(rf_tox_top_boruta_random_6_25000,
             "Toxicity",
             rf_tox_boruta_noipi_6,
             "(99.1 %ile)", 
             "B3GAT1-CCR4-CD28-EOMES-TGFB1-TNF",
             2)
```

#tox high boruta 5 graph
```{r}
rf_tox_high_noipi_boruta_5 <- readRDS(file = "../Outputs/rf_tox_high_noipi_boruta_5.RData")
rf_tox_high_noipi_random_boruta_5_25000 <- readRDS(file = "../Outputs/rf_tox_high_noipi_random_boruta_5_25000.RData")

tox.boruta5 <- met.p.calc(rf_tox_high_noipi_random_boruta_5_25000,
                        "Toxicity",
                       tox.boruta5,
                       rf_tox_high_noipi_boruta_5)



metric_graph(rf_tox_high_noipi_random_boruta_5_25000,
             "Toxicity",
             rf_tox_high_noipi_boruta_5,
             "(99.1 %ile)", 
             "5 mRNAs",
             2)
```


#tox fulllow boruta 14 graph
```{r}
rf_tox_fulllow_noipi_boruta_14 <- readRDS(file = "../Outputs/rf_tox_fulllow_noipi_boruta_14.RData")
rf_tox_fulllow_noipi_random_boruta_14_25000 <- readRDS(file = "../Outputs/rf_tox_fulllow_noipi_random_boruta_14_25000.RData")

tox.borutafulllow <- met.p.calc(rf_tox_fulllow_noipi_random_boruta_14_25000,
                        "Toxicity",
                       tox.borutafulllow,
                       rf_tox_fulllow_noipi_boruta_14)



metric_graph(rf_tox_fulllow_noipi_random_boruta_14_25000,
             "Toxicity",
             rf_tox_fulllow_noipi_boruta_14,
             "(96.4 %ile)", 
             "14 mRNAs",
             2)
```


#tox fullmed boruta 2 graph Majority model
```{r}
rf_tox_fullmed_noipi_boruta_2 <- readRDS(file = "../Outputs/rf_tox_fullmed_noipi_boruta_2.RData")
rf_tox_fullmed_noipi_random_boruta_2_25000 <- readRDS(file = "../Outputs/rf_tox_fullmed_noipi_random_boruta_2_25000.RData")

tox.borutafullmed <- met.p.calc(rf_tox_fullmed_noipi_random_boruta_2_25000,
                        "Toxicity",
                       tox.borutafullmed,
                       rf_tox_fullmed_noipi_boruta_2)



metric_graph(rf_tox_fullmed_noipi_random_boruta_2_25000,
             "Toxicity",
             rf_tox_fullmed_noipi_boruta_2,
             "(89.0 %ile)", 
             "Boruta-Majority of runs",
             3)
```



#tox fullhigh boruta 1 graph
```{r}
rf_tox_fullhigh_noipi_boruta_1 <- readRDS(file = "../Outputs/rf_tox_fullhigh_noipi_boruta_1.RData")
rf_tox_fullhigh_noipi_random_boruta_1_25000 <- readRDS(file = "../Outputs/rf_tox_fullhigh_noipi_random_boruta_1_25000.RData")

tox.borutafullhigh <- met.p.calc(rf_tox_fullhigh_noipi_random_boruta_1_25000,
                        "Toxicity",
                       tox.borutafullhigh,
                       rf_tox_fullhigh_noipi_boruta_1)



metric_graph(rf_tox_fullhigh_noipi_random_boruta_1_25000,
             "Toxicity",
             rf_tox_fullhigh_noipi_boruta_1,
             "(93.3 %ile)", 
             "1 mRNA",
             1.5)
```




#Meta tox clinical
```{r}
rf_tox_meta_clinical <- readRDS(file = "../Outputs/rf_tox_meta_clinical.RData")
rf_tox_meta_clinical_random_25000 <- readRDS(file = "../Outputs/rf_tox_meta_clinical_random_25000.RData")

metatox.clinical <- met.p.calc(rf_tox_meta_clinical_random_25000,
                        "Toxicity",
                       metatox.clinical,
                       rf_tox_meta_clinical)



metric_graph(rf_tox_meta_clinical_random_25000,
             "Toxicity",
             rf_tox_meta_clinical,
             "(94.2 %ile)", 
             "Clinical",
             5)

```



#Meta tox total
```{r}
rf_tox_meta <- readRDS(file = "../Outputs/rf_tox_meta.RData")
rf_tox_meta_random_25000 <- readRDS(file = "../Outputs/rf_tox_meta_random_25000.RData")

metatox.total <- met.p.calc(rf_tox_meta_random_25000,
                        "Toxicity",
                       metatox.total,
                       rf_tox_meta)



metric_graph(rf_tox_meta_random_25000,
             "Toxicity",
             rf_tox_meta,
             NULL, 
             "All mRNA",
             3)

```



#Meta tox full top list
```{r}
rf_tox_meta_fulltoplist <- readRDS(file = "../Outputs/rf_tox_meta_fulltoplist.RData")
rf_tox_meta_fulltoplist_random_25000 <- readRDS(file = "../Outputs/rf_tox_meta_random_25000.RData")

metatox.fulltoplist <- met.p.calc(rf_tox_meta_fulltoplist_random_25000,
                        "Toxicity",
                       metatox.fulltoplist,
                       rf_tox_meta_fulltoplist)



metric_graph(rf_tox_meta_fulltoplist_random_25000,
             "Toxicity",
             rf_tox_meta_fulltoplist,
             "(100 %ile)", 
             "CD80-CEACAM1-SPI1-SPN-HAVCR2",
             3)

```


#Meta tox boruta list
```{r}
rf_tox_meta_boruta_2 <- readRDS(file = "../Outputs/rf_tox_meta_boruta_2.RData")
rf_tox_meta_random_boruta_2_25000 <- readRDS(file = "../Outputs/rf_tox_meta_random_boruta_2_25000.RData")

metatox.boruta <- met.p.calc(rf_tox_meta_random_boruta_2_25000,
                        "Toxicity",
                       metatox.boruta,
                       rf_tox_meta_boruta_2)



metric_graph(rf_tox_meta_random_boruta_2_25000,
             "Toxicity",
             rf_tox_meta_boruta_2,
             "(97.8 %ile)", 
             "IL-21 - SPI1",
             7.5)

```



#Meta tox fulllow boruta list
```{r}
rf_tox_meta_fulllow_boruta_6 <- readRDS(file = "../Outputs/rf_tox_meta_fulllow_boruta_6.RData")
rf_tox_meta_fulllow_random_boruta_6_25000 <- readRDS(file = "../Outputs/rf_tox_meta_fulllow_random_boruta_6_25000.RData")

metatox.borutafulllow <- met.p.calc(rf_tox_meta_fulllow_random_boruta_6_25000,
                        "Toxicity",
                       metatox.borutafulllow,
                       rf_tox_meta_fulllow_boruta_6)



metric_graph(rf_tox_meta_fulllow_random_boruta_6_25000,
             "Toxicity",
             rf_tox_meta_fulllow_boruta_6,
             NULL, 
             "6 mRNAs",
             7.5)

```


#Meta tox fullmed boruta list
```{r}
rf_tox_meta_fullmed_boruta_2 <- readRDS(file = "../Outputs/rf_tox_meta_fullmed_boruta_2.RData")
rf_tox_meta_fullmed_random_boruta_2_25000 <- readRDS(file = "../Outputs/rf_tox_meta_fullmed_random_boruta_2_25000.RData")

metatox.borutafullmed <- met.p.calc(rf_tox_meta_fullmed_random_boruta_2_25000,
                        "Toxicity",
                       metatox.borutafullmed,
                       rf_tox_meta_fullmed_boruta_2)



metric_graph(rf_tox_meta_fullmed_random_boruta_2_25000,
             "Toxicity",
             rf_tox_meta_fullmed_boruta_2,
             NULL, 
             "Boruta-Majority of runs",
             7.5)

```



#Meta tox fullhigh boruta list
```{r}
rf_tox_meta_fullhigh_boruta_1 <- readRDS(file = "../Outputs/rf_tox_meta_fullhigh_boruta_1.RData")
rf_tox_meta_fullhigh_random_boruta_1_25000 <- readRDS(file = "../Outputs/rf_tox_meta_fullhigh_random_boruta_1_25000.RData")

metatox.borutafullhigh <- met.p.calc(rf_tox_meta_fullhigh_random_boruta_1_25000,
                        "Toxicity",
                       metatox.borutafullhigh,
                       rf_tox_meta_fullhigh_boruta_1)



metric_graph(rf_tox_meta_fullhigh_random_boruta_1_25000,
             "Toxicity",
             rf_tox_meta_fullhigh_boruta_1,
             "(74.9 %ile)", 
             "1 mRNA",
             3)

```



#adj train meta test toxicity
```{r}
rf_tox_adjtrain_metatest <- readRDS(file = "../Outputs/rf_tox_top_metatox.RData")
rf_tox_adjtrain_metatest_random <- readRDS(file = "../Outputs/rf_tox_top_metatox_random_25000.RData")

adj_train_tox <- met.p.calc(rf_tox_adjtrain_metatest_random,
                        "Toxicity",
                       adj_train_rec,
                       rf_tox_adjtrain_metatest)



metric_graph(rf_tox_adjtrain_metatest_random,
             "Toxicity",
             rf_tox_adjtrain_metatest,
             "(93.2 %ile)", 
             "Adj Train Meta Test Tox",
             5)
```



#meta train adj test toxicity
```{r}
rf_tox_metatrain_adjtest <- readRDS(file = "../Outputs/rf_tox_meta_fulltoplist_adjtox.RData")
rf_tox_metatrain_adjtest_random <- readRDS(file = "../Outputs/rf_tox_meta_fulltoplist_adjtox_random_25000.RData")

meta_train_tox <- met.p.calc(rf_tox_metatrain_adjtest_random,
                        "Toxicity",
                       meta_train_tox,
                       rf_tox_metatrain_adjtest)



metric_graph(rf_tox_metatrain_adjtest_random,
             "Toxicity",
             rf_tox_metatrain_adjtest,
             "(70.0% %ile)", 
             "Meta Train Adj Test Tox",
             2)
```



#tox top 3 metagene graph
```{r}
rf_tox_metgenes_noipi_3 <- readRDS(file = "../Outputs/rf_tox_metgenes_noipi_3.RData")
rf_tox_metgenes_noipi_random_3_25000 <- readRDS(file = "../Outputs/rf_tox_metgenes_noipi_random_3_25000.RData")

tox.metagenes <- met.p.calc(rf_tox_metgenes_noipi_random_3_25000,
                        "Toxicity",
                       tox.metagenes,
                       rf_tox_metgenes_noipi_3)



metric_graph(rf_tox_metgenes_noipi_random_3_25000,
             "Toxicity",
             rf_tox_metgenes_noipi_3,
             NULL, 
             "CD8A-CD45RB-TNFRSF14",
             2.5)
```


#tox top 5 metastatic
```{r}
rf_met_tox_noipi_top_5_0 <- readRDS(file = "../Outputs/rf_met_tox_noipi_top_5_0.RData")
rf_met_tox_noipi_top_random_5_0_25000 <- readRDS(file = "../Outputs/rf_met_tox_noipi_top_random_5_0_25000.RData")

tox.metastatic <- met.p.calc(rf_met_tox_noipi_top_random_5_0_25000,
                        "Toxicity",
                       tox.metastatic,
                       rf_met_tox_noipi_top_5_0)



metric_graph(rf_met_tox_noipi_top_random_5_0_25000,
             "Toxicity",
             rf_met_tox_noipi_top_5_0,
             NULL, 
             "TNFRSF18-VTCN1-CCR4-AHR-TIGIT",
             2.3)
```











