---
title: "tableone"
author: "Noah Lepola"
date: "2024-12-31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tableone)
library(tidyverse)

```


Loading files
```{r}
load(file = "../Outputs/pt.char")
load(file = "../Outputs/pt.status_no_ipi")

pt.char <- pt.char %>%
  filter(Sample %in% pt.status$Sample)
```


Combining everything to be used in the table
```{r}
pt.char.status <- full_join(pt.status, pt.char)

pt.char.status <- pt.char.status %>% select(!Sample)
```

Splitting data to be used in different outcome tables
```{r}
tc.tox <-filter(pt.char.status, `Reason.for.discontinuation` == 
      "Therapy complete" | `Reason.for.discontinuation` == "Toxicity") 

tc.rec <-filter(pt.char.status, `Reason.for.discontinuation` ==
      "Therapy complete" | `Reason.for.discontinuation` == "Progression")
```

Creating objects for first table
```{r}
vars <- c("Sex", "Reason.for.discontinuation", "Age", "BMI (kg/m2)", "Platelets (K/uL)", "LDH (U/L)",
           "Stage", "Therapy")
```


Making Table One separated by cohort
```{r}
pt.char.status[pt.char.status$Reason.for.discontinuation != "Therapy complete" & pt.char.status$Reason.for.discontinuation != "Toxicity" & pt.char.status$Reason.for.discontinuation != "Progression", "Reason.for.discontinuation"] <- "Other"

pt.char.status[pt.char.status$Cohort == "Adj Validation", "Cohort"] <- "Validation"
pt.char.status[pt.char.status$Cohort == "Adj", "Cohort"] <- "Exploratory"


cohort.strat <- CreateTableOne(vars = vars, strata = "Cohort",
                               data = pt.char.status, test = TRUE)
cohort.strat

knitr::kable(print(cohort.strat, showAllLevels = TRUE))
```

Creating objects for second and third table
```{r}

vars23 <- c("Age", "BMI (kg/m2)", "Platelets (K/uL)", "LDH (U/L)",
           "Stage", "Therapy")
```

Making Table One separated by outcome (therapy complete vs toxicity)
```{r}
TCvsTOX.strat <- CreateTableOne(vars = vars23, strata = 
                "Reason.for.discontinuation", data = tc.tox, test = TRUE) 

TCvsTOX.strat 
```


Making Table One separated by outcome (therapy complete vs recurrence)
```{r}
tc.rec$Reason.for.discontinuation <- factor(tc.rec$Reason.for.discontinuation,
                levels = c("Therapy complete", "Progression"))

TCvsREC.strat <- CreateTableOne(vars = vars23, strata =
                "Reason.for.discontinuation", data = tc.rec, test = TRUE)
  
TCvsREC.strat

```

